---
  output: github_document
---


[![Travis build status](https://travis-ci.com/muschellij2/upstrap.svg?branch=master)](https://travis-ci.com/muschellij2/upstrap)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/upstrap?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/upstrap)
[![Coverage status](https://codecov.io/gh/muschellij2/upstrap/branch/master/graph/badge.svg)](https://codecov.io/gh/muschellij2/upstrap)
<!-- README.md is generated from README.Rmd. Please edit that file -->

# upstrap
Materials accompanying the upstrap paper including vignette (.Rmd, .pdf, .html), Sleep Heart Health Study (SHHS) data, 
and figure used for the vignette

An R package called upstrap and additional code will be added as it becomes available

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# upstrap Package: 
The goal of `upstrap` is to provide the upstrap resamples data with a sample size larger than the original sample size.  This method allows users to see behavior of estimators in increasing sample sizes, commonly done for sample size calculation.

## Installation

You can install `upstrap` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/upstrap")
```


